\lstnewenvironment{prompt}{%
    \lstset{
      language={},
      basicstyle=\ttfamily,
      extendedchars=true,
        breaklines=true,
        breakatwhitespace=true,
        breakindent=0pt,
        % border:
        frame=single,
        framerule=0.25pt,
        framesep=5pt,
        xleftmargin=6pt,
        xrightmargin=6pt,
        caption={Most recent version of the prompt. (L) is a slot for the description of the formal language (see Listing \ref{listing:L}).},captionpos=b,label={listing:prompt}
    }
}{}

\begin{prompt}
Your task is to interpret the meaning of a user utterance and output it in a particular semantic representation. Only output the semantic representation without any surrounding content.

SEMANTIC REPRESENTATION

(L)

EXAMPLES

why? -> Ask(Why())
why do you think this person is introverted -> Ask(Why(Not(Extraverted())))
why do you think this person likes danceable music? -> Ask(Why(HighValue(danceability_mean)))
why do you think this person likes music that is not danceable? -> Ask(Why(Not(HighValue(danceability_mean))))
why do you think this person likes loud music? -> Ask(Why(HighValue(loudness_mean)))
why do you think this person likes silent music? -> Ask(Why(Not(HighValue(loudness_mean))))
I don't understand -> ICM(understanding, negative)
so what? -> ICM(understanding, negative)
OK -> ICM(acceptance, positive)
how does liking music that is not danceable explain being introverted? -> Ask(Why(Explains(Not(HighValue(danceability_mean)), Not(Extraverted()))))
does the the fact that the person likes music that is not danceable support the assessment that the person is extraverted? -> Ask(BooleanQuestion(Supports(Not(HighValue(danceability_mean)), Extraverted())))
Which audio properties do you consider? -> Ask(WhQuestion(FactorsConsidered))
Does listening to Patti Smith affect your assessment? -> Ask(WhQuestion(FactorsConsidered))
do you think this person is extraverted? -> Ask(BooleanQuestion(Extraverted()))
next case please -> None
increase the volume -> None
\end{prompt}
